Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-04-23 draft/paper1_jenny.tex
more edits from Jenny

    Massive galaxies are unique laboratories for studying both cosmology and galaxy 
    formation. 
    Simulations of structure formation within the context of the $\Lambda$-CDM 
    cosmological model make predictions for the hierarchical growth of dark matter 
    halos and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many 
    open questions regarding the star-formation history, mass assembly process, and 
    structural evolution of massive galaxies. 
    Massive galaxies are thought to grow according to a ``two-phase'' formation 
    scenario (e.g. \citealt{Oser2010, Oser2012}). 
    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies 
    (ETGs) undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk 
    instabilities or gas rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
    Observationally, the progenitors of ETGs are thought to correspond to the 
    so-called ``red nuggets'' (e.g. \citealt{Damjanov2009}) which have smaller 
    effective radii ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, vanDokkum2008, 
    Cimatti2008}), slightly higher central velocity dispersion and stellar mass 
    density (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like 
    morphologies (e.g. \citealt{vanderWel2011}) than their local descendants 
    (e.g. \citealt{Bezanson2009, vanDokkum2010}).

    Following this initial epoch of early formation, feedback from stars and/or AGN 
    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quench star formation in 
    massive galaxies and a large fraction of these massive progenitors become 
    quiescent at $z>1$ (e.g. \citealt{Bezanson2009, Kriek2016}). 
    The second phase in the ``two-phase'' formation scenario is driven by 
    non-dissipative processes such as dry mergers with other galaxies 
    (e.g. \citealt{Naab2006, Khochfar2006}). 
    \update{
    To explain the observed significant increase of $R_{\mathrm{e}}$ (e.g. 
    \citealt{Newman2012, vdWel2014}) as well as the build-up of the outer stellar 
    halos of ETGs (e.g. \citealt{Szomoru2012, Patel2013}), the ``two-phase'' 
    scenario suggests that minor mergers should dominate the mass assembly during 
    the second phase (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, 
    Laporte2013}).
    More importantly, both numerical simulation (e.g. \citealt{Oser2010}) and 
    semi-analytic model (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
    mass fraction of the accreted component should increase with total stellar mass, 
    although different models still predict somewhat different values at fixed 
    stellar mass (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
    According to the recent results from Illustris \footnote{
    \texttt{http://www.illustris-project.org/}} simulation 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}), the fraction of the 
    accreted mass increases significantly with total stellar mass at \logms{}$>11.0$, 
    and the accreted component starts to dominate the stellar mass budget 
    ($f_{\mathrm{accreted}}>0.5$) at \logms{}$>11.5$ (\citealt{RodriguezGomez2016}).
    }
%% ------------------------------------------------------------------------------------ %%

    \update{
    At the same time, some of these ``two-phase'' scenario's predictions still have 
    little observational constraint. 
    One-dimensional analysis used to conclude that \ser{} law can reasonably describe  
    the surface brightness (or stellar mass density) profiles of nearby massive 
    elliptical galaxies (e.g. \citealt{Kormendy2009}; except for the most central 
    region), and the \ser{} index seems to increase with total luminosity (or stellar 
    mass; e.g. \citealt{Graham2013}). 
    There was also suggestion that elliptical galaxies can be divided into two groups
    based on how well their 1-D surface brightness profiles can be described by \ser{}
    law (e.g. \citealt{Schombert2015}). 
    Meanwhile, recent two-dimensional analysis points out that the stellar distributions 
    of massive ETGs are better fit by multiple-component models 
    (e.g. \citealt{Huang2013a, Oh2017}). 
    However, it is still not clear whether these 1-D or 2-D results are consistent with 
    the ``two-phase'' scenario. 
    One of the main limitation here is that one needs very deep observations for large 
    sample of massive ETGs to correctly estimate their total stellar mass 
    (e.g. \citealt{Bernardi2013, DSouza2014}) and study the assembly history via 
    their accreted halos (e.g. \citealt{Capaccioli2015, Iodice2016, Iodice2017}).
    Currently, such works are often limited by the shallow images such as the ones from
    the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}) or the small 
    sample size. 
    }

@@

    \update{
    For objects without a spectroscopic redshift, we match them with the central 
    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius, 
    and keep the matched objects with useful red-sequence photo-$z$ 
    ($0.3 \leq z_{\lambda} < 0.5$) in the final sample. 
    These galaxies are the best candidates for BCGs in clusters selected from 
    SDSS DR8 data (\citealt{SDSSDR8}) via a well-tested red-sequence method. 
    The accuracy of the red-sequence photo-$z$ is sufficient (median 
    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with spec-$z$) 
    for the goal of this work.
    }
    The \redm{} catalog provides an additional 133 unique redshifts for massive 
    galaxies in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

@@

    For physical (e.g.\ late-stage major merger) and unphysical (e.g.\ nearby foreground 
    galaxy or bright star) reasons, we can not extract reliable 1-D profiles for a small 
    fraction of massive galaxies because they are heavily masked out. 
    \update{
    This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
    the sample.
    }
    %It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
    %\nbcg{} sample. 
    It is worth noting that this excludes most major-merging massive galaxies.

    \update{
    Given our exquisite profiles out to 100 kpc, the definition and meaning of ``total'' 
    magnitude (and stellar mass) becomes more interesting.
    With the help of the \m2l{} estimated in the next section (\S \ref{sec:mstar}), 
    we can integrate the profile out to certain radii, and estimate the stellar mass 
    within.  
    Motivated by the ``two-phase'' scenario, we will consider two benchmark physical 
    apertures throughout this work:
    }

>>>>

    Massive galaxies are unique laboratories for studying both cosmology and galaxy 
    formation. 
    Simulations of structure formation within the context of the $\Lambda$-CDM 
    cosmological model make predictions for the hierarchical growth of dark matter 
    halos and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many 
    open questions regarding the star-formation history, mass assembly process, and 
    structural evolution of massive galaxies. 
    Massive galaxies are thought to grow according to a ``two-phase'' formation 
    scenario (e.g. \citealt{Oser2010, Oser2012}). 
    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies 
    (ETGs) undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk 
    instabilities or gas-rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
    Observationally, the progenitors of ETGs are thought to correspond to the 
    so-called ``red nuggets'' (e.g. \citealt{Damjanov2009}) which have smaller 
    effective radii ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, vanDokkum2008, 
    Cimatti2008}), slightly higher central velocity dispersion and stellar mass 
    density (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), and more disk-like 
    morphologies (e.g. \citealt{vanderWel2011}) than their local descendants 
    (e.g. \citealt{Bezanson2009, vanDokkum2010}).

    Following this initial epoch of early formation, feedback from stars and/or AGN 
    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quench star formation in 
    massive galaxies and a large fraction of these massive progenitors become 
    quiescent at $z>1$ (e.g. \citealt{Bezanson2009, Kriek2016}). 
    The second phase in the ``two-phase'' formation scenario is driven by 
    non-dissipative processes such as dry mergers with other galaxies 
    (e.g. \citealt{Naab2006, Khochfar2006}). 
    \update{
    To explain the observed significant increase of $R_{\mathrm{e}}$ (e.g. 
    \citealt{Newman2012, vdWel2014}) as well as the build-up of the outer stellar 
    halos of ETGs (e.g. \citealt{Szomoru2012, Patel2013}), the ``two-phase'' 
    scenario suggests that minor mergers should dominate the mass assembly during 
    the second phase (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, 
    Laporte2013}).
    Both numerical simulation (e.g. \citealt{Oser2010}) and 
    semi-analytic modeling (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
    mass fraction in the accreted component should increase with total stellar mass, 
    although details still differ between models (e.g. \citealt{Lackner2012, Cooper2013, Qu2017}).
    According to recent results from the Illustris \footnote{
    \texttt{http://www.illustris-project.org/}} simulation 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}), the fraction of  
    accreted mass increases significantly with total stellar mass at \logms{}$>11.0$, 
    and the accreted component starts to dominate the stellar mass budget 
    ($f_{\mathrm{accreted}}>0.5$) at \logms{}$>11.5$ (\citealt{RodriguezGomez2016}).
    }
%% ------------------------------------------------------------------------------------ %%

    \update{
    Given the success of this two-phase scenario in explaining trends like overall size growth, it is 
    time to confront their predictions with additional observations using local galaxy mass profiles. Some 
    progress has been made. One-dimensional analysis has shown that a \ser{} law well-describes 
    the surface brightness (or stellar mass density) profiles of most nearby massive 
    elliptical galaxies (e.g. \citealt{Kormendy2009}; except for the most central 
    region), with the \ser{} index increasing with total luminosity (e.g. \citealt{Graham2013}).
	But, the situation may be more complicated, with a suggestion from \citet{Schombert2015} that there are actually 
    two families of light profiles. Two-dimensional analysis, meanwhile, finds that the stellar distributions 
    of massive ETGs are better fit by multiple-component models 
    (e.g. \citealt{Huang2013a, Oh2017}). 
    To really confront the two-phase model requires very deep observations for large 
    samples of massive ETGs to correctly estimate their total stellar mass 
    (e.g. \citealt{Bernardi2013, DSouza2014}) and study their assembly history via 
    their accreted halos (e.g. \citealt{Capaccioli2015, Iodice2016, Iodice2017}).
    Currently, such work is limited by the depth of imaging from large-area surveys such as the 
    Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}) or the small 
    area of deeper imaging. 
    }

@@

    \update{
    Objects without a spectroscopic redshift are matched with the central 
    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius. 
    We keep the matched objects with useful red-sequence photo-$z$ 
    ($0.3 \leq z_{\lambda} < 0.5$) in the final sample. 
    These galaxies are the best candidates for centrals in clusters selected from 
    SDSS DR8 data (\citealt{SDSSDR8}) via a well-tested red-sequence method. 
    The accuracy of the red-sequence photo-$z$ is sufficient (median 
    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with spec-$z$) 
    for the goal of this work.
    }
    The \redm{} catalog provides an additional 133 unique redshifts for massive 
    galaxies in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

@@

    For physical (e.g.\ late-stage major merger) and nuisance (e.g.\ nearby foreground 
    galaxy or bright star) reasons, we cannot extract reliable 1-D profiles for a small 
    fraction of massive galaxies because they are heavily masked out. 
    \update{
    This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
    the sample.
    }
    %It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
    %\nbcg{} sample. 
    It is worth noting that this excludes most major-merging massive galaxies.

    \update{
    Given our exquisite profiles that extend to 100 kpc, the definition and meaning of ``total'' 
    magnitude (and stellar mass) becomes more nuanced.
    With the help of the \m2l{} estimated in the next section (\S \ref{sec:mstar}), 
    we integrate the profile to a range of radii, and estimate the stellar mass 
    within these different apertures.  
    Motivated by the two-phase scenario, we will consider two benchmark physical 
    apertures throughout this work:
    }
